\mytitle

### 2012-02-22 papers/SAS2012/implicitization.tex
Création d'une partie \appendix
Pour l'instant, le découpage est très arbitraire, mais au moins on n'est
pas loin des 15 pages.
Compactage

\item We conducted extensive experiments with this tool, on real-life programs: (i) fixing the abstract domain, varying the iteration technique (\S~\ref{sec:compare_techniques}) (ii) fixing the iteration technique, varying the abstract domain (\S\ref{sec:compare_domains}).
\end{enumerate}

@@

More generally, this analysis method considers an ascending sequence of subsets of the transitions in the loop body (left side of Fig.~\ref{fig:multigraph});
for each subset, an inductive invariant is computed for the program restricted to it.
The starting subset are the transitions reachable in one step from the loop initialization.
If for a given subset $S$ in the sequence, no transitions outside $S$ are reachable from the inductive invariant attached to $S$, then iterations stop;
otherwise, add these transitions to $S$ and iterate more.
Termination ensues from the finiteness of the control-flow graph.

@@

Algorithm~\ref{algo:combined} performs Guided static analysis on the implicitly represented multigraph.

The current working subset of paths, noted $P$ and initially empty, is
stored using a compact representation, such as binary decision
diagrams. We also maintain two sets of control points:
\begin{itemize}
	\item $A'$ contains the points in $P_R$ that may be the starting points of new
		feasible paths.
	\item $A$ contains the points in $P_R$ on which we apply the ascending iterations.
	Each time the abstract value of a control point $p$ is updated, $p$ is
	inserted in both $A$ and $A'$.
\end{itemize}

@@

We distinguish three phases in the main loop of the analysis:
\begin{enumerate}
\item \label{step:addingpaths} We start finding a new relevant subset
  $P \cup P'$ of the graph.
  Either the previous iteration or the initialization lead us to a
  state where there are no more paths in the previous subset $P$,
  starting at $p_i$, that make the abstract values of the successors
  grow (otherwise, the SMT solver would not have answered
  ``\emph{unsat}''). Narrowing iterations preserve this property.
  However, there may exist such paths in the entire multigraph, that
  are not in $P$. This phase computes these paths and adds them to
  $P'$. This phase is described in~\ref{subsec:addingpaths}
  and corresponds to lines in~\ref{alg=start-add-paths} to
  \ref{alg=end-add-paths} in Algorithm~\ref{algo:combined}.
\item \label{step:ascending} Given a new subset $P$, we search for paths starting at point
  $p_i \in P_R$, such that these paths are in $P$, i.e are included in
  the working subgraph. Each time we find a path, we update the
  abstract value of the destination point of the path. This is the
  phase explained in~\ref{subsec:ascending}, and corresponds to
  lines~\ref{alg=start-ascending} to~\ref{alg=end-ascending} in
  Algorithm~\ref{algo:combined}.
\item  \label{step:narrowing} We perform narrowing iterations the usual way
  (line~\ref{alg=narrowing} in algorithm~\ref{algo:combined}) and
  reiterate from step 1 unless there are no more points to explore,
  i.e. $A' = \emptyset$.
\end{enumerate}

@@

Suppose the main loop of the rate limiter contains a nested loop:
\lstinputlisting{rlim_int_loop.c}

@@

\begin{table}[!h]
      \centering
      \begin{tabular}{|l|r|r|r|r|r|r|r|} \hline
        \multicolumn{1}{|c|}{} &
        \multicolumn{2}{c|}{Size} &
        \multicolumn{5}{c|}{Execution time (seconds)} \\ \hline
        \multicolumn{1}{|c|}{Name} & 
        \multicolumn{1}{c|}{kLOC}  & 
        \multicolumn{1}{c|}{$|P_R|$}  &
        \multicolumn{1}{c|}{\textbf{S}} &
        \multicolumn{1}{c|}{\textbf{G}} &
        \multicolumn{1}{c|}{\textbf{PF}} &
        \multicolumn{1}{c|}{\textbf{G+PF}} &
	\multicolumn{1}{c|}{\textbf{DIS}} \\ 
        \hline
        % M-x align RET powers ;-).
a2ps-4.14      & 55  & 2012  & 64  & 17  & 66   & 175  & 512   \\
gawk-4.0.0     & 59  & 902   & 59  & 8   & 18   & 43   & 129   \\
gnuchess-6.0.0 & 38  & 1222  & 112 & 21  & 122  & 374  & 866   \\
gnugo-3.8      & 83  & 2801  & 155 & 31  & 128  & 382  & 1403  \\
grep-2.9       & 35  & 820   & 50  & 12  & 21   & 58   & 307   \\
gzip-1.4       & 27  & 494   & 63  & 12  & 36   & 97   & 617   \\
lapack-3.3.1   & 954 & 16422 & 721 & 246 & 2690 & 6052 & 22222 \\
make-3.82      & 34  & 993   & 22  & 7   & 32   & 83   & 255   \\
sed-4.2        & 23  & 292   & 35  & 7   & 23   & 69   & 521   \\
tar-1.26       & 73  & 1712  & 270 & 39  & 110  & 304  & 1164  \\
% TODO: mettre à jour les chiffres ?
	\hline
\end{tabular}
\caption{List of analyzed open-source projects, with their respective number of
lines of code, and their number of control points in $P_R$}
\label{fig:projects}
\end{table}

@@

\phantomsection\addcontentsline{toc}{section}{References} 
\bibliographystyle{splncs03}
\bibliography{implicitization}
\end{document}

>>>>

\item We conducted extensive experiments with this tool, on real-life programs: (i) fixing the abstract domain, varying the iteration technique (\S\ref{sec:compare_techniques}) (ii) fixing the iteration technique, varying the abstract domain (\S\ref{sec:compare_domains}).
\end{enumerate}

@@

More generally, this analysis method considers an ascending sequence of subsets of the transitions in the loop body \avirer{(left side of Fig.~\ref{fig:multigraph})};
for each subset, an inductive invariant is computed for the program restricted to it.
The starting subset are the transitions reachable in one step from the loop initialization.
If for a given subset $S$ in the sequence, no transitions outside $S$ are reachable from the inductive invariant attached to $S$, then iterations stop;
otherwise, add these transitions to $S$ and iterate more.
Termination ensues from the finiteness of the control-flow graph.

@@

Algorithm~\ref{algo:combined} performs Guided static analysis on the implicitly represented multigraph.
%
The current working subset of paths, noted $P$ and initially empty, is
stored using a compact representation, such as binary decision
diagrams. We also maintain two sets of control points:
\begin{compactitem}
	\item $A'$ : points in $P_R$ that may be the starting points of new
		feasible paths.
	\item $A$ : points in $P_R$ on which we apply the ascending iterations.
	When the abstract value of a control point $p$ is updated, $p$ is
	added to both $A$ and $A'$.
\end{compactitem}

@@

We distinguish three phases in the main loop of the analysis:
\begin{compactenum}
\item \label{step:addingpaths} We start finding a new relevant subset
  $P \cup P'$ of the graph.
  Either the previous iteration or the initialization lead us to a
  state where there are no more paths in the previous subset $P$,
  starting at $p_i$, that make the abstract values of the successors
  grow (otherwise, the SMT solver would not have answered
  ``\emph{unsat}''). Narrowing iterations preserve this property.
  However, there may exist such paths in the entire multigraph, that
  are not in $P$. This phase computes these paths and adds them to
  $P'$. This phase is described in~\ref{subsec:addingpaths}
  and corresponds to lines in~\ref{alg=start-add-paths} to
  \ref{alg=end-add-paths} in Algorithm~\ref{algo:combined}.
\item \label{step:ascending} Given a new subset $P$, we search for paths starting at point
  $p_i \in P_R$, such that these paths are in $P$, i.e are included in
  the working subgraph. Each time we find a path, we update the
  abstract value of the destination point of the path. This is the
  phase explained in~\ref{subsec:ascending}, and corresponds to
  lines~\ref{alg=start-ascending} to~\ref{alg=end-ascending} in
  Algorithm~\ref{algo:combined}.
\item  \label{step:narrowing} We perform narrowing iterations the usual way
  (line~\ref{alg=narrowing} in algorithm~\ref{algo:combined}) and
  reiterate from step 1 unless there are no more points to explore,
  i.e. $A' = \emptyset$.
\end{compactenum}

@@

Suppose the main loop of the rate limiter contains a nested loop like:
\lstinputlisting{rlim_int_loop.c}

@@

\begin{table}[!h]
      \centering
      \begin{tabular}{|l|r|r|r|r|r|r|r|} \hline
        \multicolumn{1}{|c|}{} &
        \multicolumn{2}{c|}{Size} &
        \multicolumn{5}{c|}{Execution time (seconds)} \\ \hline
        \multicolumn{1}{|c|}{Name} & 
        \multicolumn{1}{c|}{kLOC}  & 
        \multicolumn{1}{c|}{$|P_R|$}  &
        \multicolumn{1}{c|}{\textbf{S}} &
        \multicolumn{1}{c|}{\textbf{G}} &
        \multicolumn{1}{c|}{\textbf{PF}} &
        \multicolumn{1}{c|}{\textbf{G+PF}} &
	\multicolumn{1}{c|}{\textbf{DIS}} \\ 
        \hline
        % M-x align RET powers ;-).
a2ps-4.14      & 55  & 2012  & 64  & 17  & 66   & 175  & 512   \\
gawk-4.0.0     & 59  & 902   & 59  & 8   & 18   & 43   & 129   \\
gnuchess-6.0.0 & 38  & 1222  & 112 & 21  & 122  & 374  & 866   \\
gnugo-3.8      & 83  & 2801  & 155 & 31  & 128  & 382  & 1403  \\
grep-2.9       & 35  & 820   & 50  & 12  & 21   & 58   & 307   \\
gzip-1.4       & 27  & 494   & 63  & 12  & 36   & 97   & 617   \\
lapack-3.3.1   & 954 & 16422 & 721 & 246 & 2690 & 6052 & 22222 \\
make-3.82      & 34  & 993   & 22  & 7   & 32   & 83   & 255   \\
sed-4.2        & 23  & 292   & 35  & 7   & 23   & 69   & 521   \\
tar-1.26       & 73  & 1712  & 270 & 39  & 110  & 304  & 1164  \\
% TODO: mettre à jour les chiffres ?
	\hline
\end{tabular}
\caption{List of analyzed open-source projects, with their respective number of
lines of code, number of control points in $P_R$, and execution time
on various techniques\MM{TODO}}
\label{fig:projects}
\end{table}

\phantomsection\addcontentsline{toc}{section}{References} 
\bibliographystyle{splncs03}
\bibliography{implicitization}

\appendix

\section{Experimental Results}

@@

\end{document}
